Feasibility of Harvesting Power to Run a Domestic Water Meter Using Streaming Cell Technology

### 2015-12-20 paper.tex
Corrected units of conductivity

        Pressure is applied to the cell by applying mains water pressure to one end while leaving the the other open to atmosphere.
        A Honeywell pressure sensor (model 26PC15SMT) is placed across the cell to measure applied pressure.
        An Agilent precision measurement mainframe (model E5270B) is used to measure the streaming potential, streaming current and the pressure sensor's output.
        The working fluid, being tap water, had a conductivity of \SI{183}{\micro\siemens\per\metre} as measured with an EDT Instruments RE 388Tx Conductivity Meter.

>>>>

        Pressure is applied to the cell by applying mains water pressure to one end while leaving the the other open to atmosphere.
        A Honeywell pressure sensor (model 26PC15SMT) is placed across the cell to measure applied pressure.
        An Agilent precision measurement mainframe (model E5270B) is used to measure the streaming potential, streaming current and the pressure sensor's output.
        The working fluid, being tap water, had a conductivity of \SI{183}{\micro\siemens\per\centi\metre} as measured with an EDT Instruments RE 388Tx Conductivity Meter.
